Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-05-10 Moltres.tex
I prefer capitalized Fig, Table, etc.

In Moltres, neutrons are described with time-dependent multi-group diffusion theory as shown
in \cref{eq:neutrons}:

@@

Delayed neutron precursors are described by \cref{eq:precursors}:

@@

As a proof of concept and to ease resolution of strong transient gradients in
temperature between fuel and moderator, the physical three dimensional problem
is reduced to a two dimensional axisymmetric model. The model molten salt
reactor is based on the \gls{MSRE}. To approximately simulate the lattice
structure of the \gls{MSRE}, a geometry is constructed with 14 repeating
fuel-moderator regions, as shown in \cref{fig:geom}. The fuel and moderator
radii are chosen such that the resulting area/volume fraction of fuel is .225 as
for the \gls{MSRE}.

@@

The fuel composition is based on the \gls{BOL} enriched uranium composition in the \gls{MSRE}
and is given in \cref{table:comp} \cite{robertson_msre_1965}.

@@

Group fluxes are shown in \cref{fig:group1,fig:group2}. The effect of the vacuum
boundary conditions is shown clearly in the cosinusoidal shapes in radial and
axial directions. Striations are observed in both fast and thermal fluxes, with
the fast group preferring the fuel and the thermal group preferring the moderator.

@@

The effect of the advecting fuel is seen in \cref{fig:temp} where the temperature
rises steadily with increasing z-coordinate. As one might expect, the temperature
gradient is negative in the radial direction.

@@

\cref{fig:pre1} shows the concentration of the longest lived precursor in the
reactor. Not surprisingly, the channel concentrations are higher in fuel channels
with higher neutron fluxes and consequently a higher number of fission
events. Because of the small decay constant of the precursor, the maximum
concentration in any given channel occurs at the core outlet.

@@

With its much larger decay constant, the sixth and last precursor has its
maximum concentration around the center-plane of the reactor as shown in
\cref{fig:pre6}. As for all other precursors, its concentration decreases with
increasing radius and decreasing neutron flux.

>>>>

In Moltres, neutrons are described with time-dependent multi-group diffusion theory as shown
in \Cref{eq:neutrons}:

@@

Delayed neutron precursors are described by \Cref{eq:precursors}:

@@

As a proof of concept and to ease resolution of strong transient gradients in
temperature between fuel and moderator, the physical three dimensional problem
is reduced to a two dimensional axisymmetric model. The model molten salt
reactor is based on the \gls{MSRE}. To approximately simulate the lattice
structure of the \gls{MSRE}, a geometry is constructed with 14 repeating
fuel-moderator regions, as shown in \Cref{fig:geom}. The fuel and moderator
radii are chosen such that the resulting area/volume fraction of fuel is .225 as
for the \gls{MSRE}.

@@

The fuel composition is based on the \gls{BOL} enriched uranium composition in the \gls{MSRE}
and is given in \Cref{table:comp} \cite{robertson_msre_1965}.

@@

Group fluxes are shown in \Cref{fig:group1,fig:group2}. The effect of the vacuum
boundary conditions is shown clearly in the cosinusoidal shapes in radial and
axial directions. Striations are observed in both fast and thermal fluxes, with
the fast group preferring the fuel and the thermal group preferring the moderator.

@@

The effect of the advecting fuel is seen in \Cref{fig:temp} where the temperature
rises steadily with increasing z-coordinate. As one might expect, the temperature
gradient is negative in the radial direction.

@@

\Cref{fig:pre1} shows the concentration of the longest lived precursor in the
reactor. Not surprisingly, the channel concentrations are higher in fuel channels
with higher neutron fluxes and consequently a higher number of fission
events. Because of the small decay constant of the precursor, the maximum
concentration in any given channel occurs at the core outlet.

@@

With its much larger decay constant, the sixth and last precursor has its
maximum concentration around the center-plane of the reactor as shown in
\Cref{fig:pre6}. As for all other precursors, its concentration decreases with
increasing radius and decreasing neutron flux.
